Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-02-21 awipev-CO2.Rmd
temperature insitu + seafet calibration OK2

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= sfinterv[23], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[23], to= sfinterv[24], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[24], to= sfinterv[25], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[25], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
